Clines from PDE

### 2015-11-04 notes/pde-clines.Rmd

Note that if we think of $u(a,b)$ as a kernel, 
then the map $u(a,b) \mapsto \int_a^b u(a,\theta) u(\theta,b) d\theta$
is just the product of the kernel to itself;
on discretization this becomes a matrix power,
so the operator $u(a,b) \mapsto \int_a^b u(a,\theta)u(\theta,b) - u(a,b) d\theta$
```{r solve_branching}
xgrid <- setup.grid.1D(x.up=-20, x.down=20, N=100)
agrid <- setup.grid.1D(x.up=-0.5, x.down=0.5, N=30)
# determines the order the solution is in:
xab <- subset( expand.grid( x=xgrid$x.mid, a=agrid$x.mid, b=agrid$x.mid ), ( b>0 ) & (abs(a)<=abs(b)) )
find_ab <- function (ab) {
    # map into the subset of (a,b) contained in xab
    flip <- ab[,1]>ab[,2] 
    ab[flip,] <- ab[flip,] %*% cbind( c(0,1), c(1,0) )
    flop <- ( ab[,1]<0 & abs(ab[,1])>=abs(ab[,2]) )
    ab[flop,] <- ab[flop,] %*% cbind( c(0,-1), c(-1,0) )
    return(ab)
}
integral_map <- function (y,ab) {
    # the discretization of the map y(a,b) -> \int_a^b (h(a,u)*h(u,b)-h(a,b)) du
    # The key step is to do something like:
    #     1 | x y .
    #   a 2 | . . u
    #     3 | . . v
    #       +------
    #     b   1 2 3
    # --> should  return x*u + y*v,
    # the inner product of a partial row with a partial column

}
```

>>>>

Note that if we think of $u(a,b)$ as a kernel, 
then the map $u(a,b) \mapsto \int_a^b u(a,\theta) u(\theta,b) d\theta$
is similar to the product of the kernel to itself;
on discretization this becomes like a matrix power.
This is implemented in some C code.
```{r solve_branching}
source("unifprod.R")  # for the C part
integral_map <- function (x,eps) {
    # the discretization of the map y(a,b) -> \int_a^b (h(a,u)*h(u,b)-h(a,b)) du
    # x is a square matrix,
    #   eps is the grid spacing between locations
    x2 <- eps*unifprod(x)
}
xgrid <- setup.grid.1D(x.up=-20, x.down=20, N=100)
agrid <- setup.grid.1D(x.up=-0.5, x.down=0.5, N=30)
# we'll save the solution as an array,
#  with dimensions (x,a,b)
# Note we only use the upper triangle a<=b, but oh well.
soln.array <- array(0.0,dim=c(xgrid$N,agrid$N,agrid$N))

# determines the order the solution is in:
xab <- subset( expand.grid( x=xgrid$x.mid, a=agrid$x.mid, b=agrid$x.mid ), ( b>0 ) & (abs(a)<=abs(b)) )
find_ab <- function (ab) {
    # map into the subset of (a,b) contained in xab
    flip <- ab[,1]>ab[,2] 
    ab[flip,] <- ab[flip,] %*% cbind( c(0,1), c(1,0) )
    flop <- ( ab[,1]<0 & abs(ab[,1])>=abs(ab[,2]) )
    ab[flop,] <- ab[flop,] %*% cbind( c(0,-1), c(-1,0) )
    return(ab)
}
```
